EinsteinPy: A Community Python Package for General Relativity

### 2020-05-04 paper.tex
Add author

   \author{
Shreyas Bapat\inst{\ref{inst:iitm}}  % confirmed
  \and
Ritwik Saha\inst{\ref{inst:iitm}}  % confirmed
  \and
Bhavya Bhatt\inst{\ref{inst:iitm}}  % confirmed
\and
Shilpi Jain\inst{\ref{inst:iitr}}
\and
Akshita Jain\inst{\ref{inst:iitm}}
\and
Sofía Ortín Vela\inst{\ref{inst:uz}}
\and
Priyanshu Khandelwal\inst{\ref{inst:gatech}}
\and
Jyotirmaya Shivottam\inst{\ref{inst:niser}}
\and
Jialin Ma\inst{\ref{inst:gatech}}
}
   \institute{
  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India
  \label{inst:iitm}
    \and
  Department of Earth Sciences, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
  \label{inst:iitr}
    \and
  University of Zaragoza, Calle de Pedro Cerbuna, 12, 50009 Zaragoza, Spain
  \label{inst:uz}
    \and
  Georgia Institute of Technology, USA
  \label{inst:gatech}
    \and
   School of Physical Sciences, National Institute of Science Education and Research, Jatni, Khurdha, Odisha, India
   \label{inst:niser}
}

>>>>

   \author{
Shreyas Bapat\inst{\ref{inst:iitm}}  % confirmed
  \and
Ritwik Saha\inst{\ref{inst:iitm}}  % confirmed
  \and
Bhavya Bhatt\inst{\ref{inst:iitm}}  % confirmed
\and
Shilpi Jain\inst{\ref{inst:iitr}}
\and
Akshita Jain\inst{\ref{inst:iitm}}
\and
Sofía Ortín Vela\inst{\ref{inst:uz}}
\and
Priyanshu Khandelwal\inst{\ref{inst:iitm}}
\and
Jyotirmaya Shivottam\inst{\ref{inst:niser}}
\and
Jialin Ma\inst{\ref{inst:gatech}}
\and
Gim Seng Ng\inst{\ref{inst:trinity}}
\and
Pratyush Kerhalkar\inst{\ref{inst:elecmani}}
\and
Hrishikesh Sudam Sarode\inst{\ref{inst:iitm}}
\and
Rishi Sharma\inst{\ref{inst:iitm}}
\and
Manvi Gupta\inst{\ref{inst:iitm}}
\and
Divya Gupta\inst{\ref{inst:iitm}}
\and
Tushar Tyagi\inst{\ref{inst:iitm}}
\and
Tanmay Rustagi\inst{\ref{inst:iitm}}
\and
Varun Singh\inst{\ref{inst:iitm}}
\and
Saurabh Bansal\inst{\ref{inst:iitm}}
\and
Naman Tayal\inst{\ref{inst:iitm}}
\and
Abhijeet Manhas\inst{\ref{inst:iitm}}
\and
Raphael Reyna\inst{\ref{inst:calpoly}}
\and
Gaurav Kumar\inst{\ref{inst:iitm}}
\and
Govind Dixit\inst{\ref{inst:iiitl}}
\and
Ratin Kumar\inst{\ref{inst:nitk}}
\and
Sashank Mishra\inst{\ref{inst:iiita}}
\and
Alpesh Jamgade\inst{\ref{inst:bharath}}
\and
Raahul Singh\inst{\ref{inst:sri}}
\and
Rohit Sanjay\inst{\ref{inst:manipal}}
\and
Khalid Shaikh\inst{\ref{inst:yadav}}
\and
Bhavam Vidyarthi\inst{\ref{inst:manipal}}
\and
Shamanth R Nayak K\inst{\ref{inst:manipalit}}
\and
Vineet Gandham\inst{\ref{inst:manipalcs}}
\and
Nimesh Vashistha\inst{\ref{inst:manipal}}
\and
Arnav Das\inst{\ref{inst:hira}}
\and
Saurabh\inst{\ref{inst:du}}
\and
Shreyas Kalvankar\inst{\ref{inst:wagh}}
\and
Ganesh Tarone\inst{\ref{inst:vish}}
\and
Atul Mangat\inst{\ref{inst:iitree}}
}
   \institute{
  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India
  \label{inst:iitm}
    \and
  Department of Earth Sciences, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
  \label{inst:iitr}
    \and
  University of Zaragoza, Calle de Pedro Cerbuna, 12, 50009 Zaragoza, Spain
  \label{inst:uz}
    \and
  Georgia Institute of Technology, USA
  \label{inst:gatech}
  \and
   School of Mathematics and Hamilton Mathematics Institute, Trinity College Dublin, Dublin 2, Ireland  
   \label{inst:trinity} 
    \and
   School of Physical Sciences, National Institute of Science Education and Research, Jatni, Khurdha, Odisha, India
   \label{inst:niser}
   \and
   Department of Electronics and Communication Engineering, Manipal Institute of Technology, India
   \label{inst:elecmani}
   \and
   California State Polytechnic University, Pomona, USA
   \label{inst:calpoly}
   \and
   Department of Information Technology, Indian Institute of Information Technology Lucknow, India
   \label{inst:iiitl}
   \and
   National Institute of Technology Kurukshetra, India
   \label{inst:nitk}
   \and
   Department of Information Technology, Indian Institute of Information Technology Allahabad, India
   \label{inst:iiita} 
   \and
   Department of Mathematics, Bharath Institute of Higher Education and Research, Chennai, India
   \label{inst:bharath}  
   \and
   Indian Institute of Information Technology, Sri City, India
   \label{inst:sri} 
   \and
   Department of Electronics and Communication Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
   \label{inst:manipal}
   \and
   Department of Computer Engineering, Yadavrao Taskgaonkar Institute of Engineering and Technology, Mumbai University, Mumbai, Maharashtra, India
   \label{inst:yadav}
   \and
   Department of Information and Communication Technology Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
   \label{inst:manipalit}
   \and
   Department of Computer Science and Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
   \label{inst:manipalcs}
   \and
   Hiranandani Foundation, Powai, Mumbai, Maharashtra, India
   \label{inst:hira}
   \and
   Dyal Singh College, University of Delhi, New Delhi, India  
   \label{inst:du} 
   \and
   K. K. Wagh Institute of Engineering Education and Research, Nashik, Maharashtra, India  
   \label{inst:wagh}
    \and
   Department of Computer Engineering,Vishwakarma Institute of Technology,Pune, Maharashtra, India  
   \label{inst:vish} 
   \and
  Department of Electrical Engineering, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
  \label{inst:iitree}
}
